Paradigms in Physics 2.0

### 2017-06-29 paper.tex
Update on Overleaf.

The students engage with the material by solving daily quiz questions
in class, solving weekly homework problems, performing a modern
physics experiment, and writing a term paper. The daily quiz questions
help clarify the goal of each lecture. The weekly homework questions
are directly related to contemporary challenges requiring a variety
of estimation techniques. The modern physics experiment, performed
with a low cost kit (LEDs, diffraction grating, rulers, volt meter
etc.) emphasizes a quantitative approach to observation and explores
issues of experimental uncertainty. Lastly, the term paper allows
students to dive deeper into a particular contemporary challenge. The
term paper tests student's ability to make their own initial
assessment of a complex problem, and communicate their ideas with
diagrams, graphs and estimations.

>>>>

The students engage with the material by solving daily quiz questions
in class, solving weekly homework problems, performing a modern
physics experiment, and writing a term paper. The daily quiz questions
help clarify the goal of each lecture. The weekly homework questions
are directly related to contemporary challenges requiring a variety
of estimation techniques. The modern physics experiment, performed
with a low cost kit (LEDs, diffraction grating, rulers, volt meter
etc.) emphasizes a quantitative approach to observation and explores
issues of experimental uncertainty. Lastly, the term paper allows
students to dive deeper into a particular contemporary challenge. The
term paper tests students' ability to make their own initial
assessment of a complex problem, and communicate their ideas with
diagrams, graphs and estimations.
